A Jacobian-free Newton-Krylov method for cell-centred finite volume solid mechanics

### 2025-09-20 article.tex
Update gradient description related to displacement boundaries

		&&+ \sum_{d_i \in \mathcal{F}^{\text{disp}}_P} w_{f_i} |\bb{\Gamma}_{d_i}| \frac{ \bb{G}^{-1}_P \cdot \bb{d}_{d_i} }{\bb{d}_{d_i} \cdot \bb{d}_{d_i}} \otimes \left(\bb{u}_{d_i} - \bb{u}_P \right) \notag \\

@@

Traction boundary faces are excluded in Equation \ref{eq:leastSquaresGrad}, as the displacement is unknown there; this is in contrast to the default approach in OpenFOAM \citep{Jasak2011}.

@@

	 &&+  \sum_{{d_i} \in \mathcal{F}^{\text{disp}}_P} (1 - w_{d_i}) |\bb{\Gamma}_{d_i}|  \frac{\bb{d}_{d_i} \otimes \bb{d}_{d_i}}{\bb{d}_{d_i} \cdot \bb{d}_{d_i}} \notag \\

@@

As noted, boundary conditions are enforced through the discretised surface integral terms at the boundary faces. % (Equations \ref{eq:divStressDiscret} and \ref{eq:RhieChow}).
If required, the displacement $\bb{u}_{t_i}$ on a traction boundary face $t_i$ can be calculated by extrapolation from the centre of cell $P$ as
\begin{eqnarray}
	\bb{u}_{t_i} = \bb{u}_P + \bb{d}_{t_i} \cdot \left(\bb{\nabla} \bb{u} \right)_P
\end{eqnarray}
where $\bb{d}_{t_i}$ represents the vector from the centroid of cell $P$ to the centroid of the traction boundary face $t_i$.
Similarly, if required, the displacement $\bb{u}_{s_i}$ at a symmetry plane face $s_i$ is calculated using the same approach as Equation \ref{eq:symm}:
\begin{eqnarray} 
	\bb{u}_{s_i}
		&=&  \frac{1}{2} \left( \bb{u}_P + \bb{R}_{s_i} \cdot \bb{u}_P \right) \notag \\
		&=& \left (\textbf{I} - \bb{n}_{s_i} \otimes \bb{n}_{s_i} \right) \cdot \bb{u}_P
\end{eqnarray}

\subsubsection{Rhie-Chow Stabilisation}

>>>>

%		&&+ \sum_{d_i \in \mathcal{F}^{\text{disp}}_P} w_{f_i} |\bb{\Gamma}_{d_i}| \frac{ \bb{G}^{-1}_P \cdot \bb{d}_{d_i} }{\bb{d}_{d_i} \cdot \bb{d}_{d_i}} \otimes \left(\bb{u}_{d_i} - \bb{u}_P \right) \notag \\

@@

Traction and displacement boundary faces are excluded in Equation \ref{eq:leastSquaresGrad}; this is in contrast to the default approach in OpenFOAM \citep{Jasak2011}.
The effect of the prescribed boundary displacements is introduced through the compact component of the Rhie-Chow stabilisation term, described in Section \ref{sec:RhieChow}.

@@

%	 &&+  \sum_{{d_i} \in \mathcal{F}^{\text{disp}}_P} (1 - w_{d_i}) |\bb{\Gamma}_{d_i}|  \frac{\bb{d}_{d_i} \otimes \bb{d}_{d_i}}{\bb{d}_{d_i} \cdot \bb{d}_{d_i}} \notag \\

@@

%As noted, boundary conditions are enforced through the discretised surface integral terms at the boundary faces. % (Equations \ref{eq:divStressDiscret} and \ref{eq:RhieChow}).
If required, the displacement $\bb{u}_{t_i}$ on a traction boundary face $t_i$ can be calculated by extrapolation from the centre of cell $P$ as
\begin{eqnarray}
	\bb{u}_{t_i} = \bb{u}_P + \bb{d}_{t_i} \cdot \left(\bb{\nabla} \bb{u} \right)_P
\end{eqnarray}
where $\bb{d}_{t_i}$ represents the vector from the centroid of cell $P$ to the centroid of the traction boundary face $t_i$.
Similarly, if required, the displacement $\bb{u}_{s_i}$ at a symmetry plane face $s_i$ is calculated using the same approach as Equation \ref{eq:symm}:
\begin{eqnarray} 
	\bb{u}_{s_i}
		&=&  \frac{1}{2} \left( \bb{u}_P + \bb{R}_{s_i} \cdot \bb{u}_P \right) \notag \\
		&=& \left (\textbf{I} - \bb{n}_{s_i} \otimes \bb{n}_{s_i} \right) \cdot \bb{u}_P
\end{eqnarray}

\subsubsection{Rhie-Chow Stabilisation} \label{sec:RhieChow}
